---
title: R Machine Learning Codebook (Part 1)
author: JungYul Yang
date: '2020-06-02'
slug: r-machine-learning
categories:
  - R
tags: []
---

R Machine Learning Codebook (Part 1)

1. Linear Regression
- Used when response variable is 'numerical' variable

```{r}
getwd()
library(readr)
#information for data
usedcar2 <- read_csv("data/usedcar2.csv")
usedcar2
```

Encoding categorical variable

```{r}
usedcar2$Ind1 <- as.numeric(usedcar2$Color == 'white')
usedcar2$Ind2 <- as.numeric(usedcar2$Color == 'silver')
usedcar2
```

Regression Fitting

```{r}
lm_used <- lm(Price ~ Odometer + Ind1 + Ind2, data=usedcar2)
summary(lm_used)
```

Plot

```{r}
plot(lm_used,which=2)
plot(lm_used,which=1)
```

Things need to check for linear regression
1. Independence
2. Normality
3. Homoscedasticity


X variable Selection

```{r}
#both = stepwise elimination, backward = backward elimination, forward = forward selection
step_used <- step(lm_used, direction='both')
summary(step_used)
```

Interaction 

```{r}
int_used <- lm(Price ~ Odometer+Ind1+Ind2+Ind1:Odometer+Ind2:Odometer,data=usedcar2)
summary(int_used)
```

Train Test split

```{r}
set.seed(1234)
nobs=nrow(usedcar2)
#train:test = 70:30
i = sample(1:nobs, round(nobs*0.7))
train = usedcar2[i,]
test= usedcar2[-i,]
nrow(train);nrow(test)
```

Prediction and correlation

```{r}

model = lm(Price ~ Odometer + Ind1 + Ind2, data=train)
pred = predict(model, newdata=test, type = 'response')
pred
cor(test$Price,pred)^2

```

2. Logistic Regression
- Used when response variable is 'categorical' variable

```{r}
directmail <- read_csv("data/directmail.csv")
#remove all na
complete = complete.cases(directmail)
directmail <- directmail[complete,]
directmail
nobs=nrow(directmail)
#train:test = 70:30
i = sample(1:nobs, round(nobs*0.7))
train = directmail[i,]
test= directmail[-i,]
nrow(train);nrow(test)
```

Logistic Fitting

```{r}
full_model = glm(RESPOND ~ AGE+BUY18+CLIMATE+FICO+INCOME+MARRIED+OWNHOME+GENDER,
                 family='binomial',data=directmail)
summary(full_model)
```

Predict Probability
```{r}
prob_pred = predict(full_model, newdata=test, type="response")
```

ROC CURVE
```{r}
library(pROC)
roccurve <- roc(test$RESPOND ~ prob_pred)
plot(roccurve,col="red",print.auc=TRUE, print.auc.adj=c(1,-7),auc.polygon=TRUE)
```


3. Decision Trees

- Used regardless of the type of response variable

```{r}
library(readr)
titanic <- read_csv("data/titanic.csv")
titanic
```

Tree Fitting

```{r}
#class represents tree where anova represents regression tree
library(rpart)
library(rpart.plot)
D_tree <- rpart(Survived ~ Class+Sex+Age, data=titanic, method='class')
print(D_tree)
prp(D_tree, type=4, extra=2, digits=3)
```

More parameters to control

```{r}
set.seed(1234)
my.control <- rpart.control(xval=10,cp=0.001)
```

hello

