---
title: R Machine Learning Codebook (Part 2)
author: JungYul Yang
date: '2020-06-03'
slug: r-machine-learning-codebook-part-2
categories: []
tags: []
---

4. Neural Network
- used regardless of response variable, but intended to predict

```{r}
library(readr)
directmail <- read_csv("data/directmail.csv")
#remove all na
complete = complete.cases(directmail)
directmail <- directmail[complete,]
directmail
nobs=nrow(directmail)

#normalization
nor = function(x) {x-min(x)/(max(x)-min(x))}
directmail$AGE <- nor(directmail$AGE)
directmail$CLIMATE <- nor(directmail$CLIMATE)
directmail$FICO <- nor(directmail$FICO)
directmail$INCOME <- nor(directmail$INCOME)
directmail$GENDER <- as.numeric(directmail$GENDER == "F")

```


```{r}
#split
set.seed(1234)
i = sample(1:nobs, round(nobs*0.7))
train = directmail[i,]
test = directmail[-i,]
nrow(train);nrow(test)
```

Neural Network Fitting
```{r}
#stepmax : iteration, threshold: error variation, act.fact : function
library(neuralnet)
nn <- neuralnet(RESPOND ~ AGE+BUY18+CLIMATE+FICO+INCOME+MARRIED+OWNHOME+GENDER,
                data=train, hidden=3, step = 1e+05, threshold = 0.01,
                act.fct = 'logistic', linear.output=F)
plot(nn)
```


Prediction
```{r}
pred <- compute(nn, covariate=test[,-1])
```


5. Ensemble
(1) Bagging

```{r}
german = read.table("data/germandata.txt",header=T)
german$numcredits = factor(german$numcredits)
german$residence = factor(german$residence)
german$residpeople = factor(german$residpeople)
summary(german)

```

Bagging Fitting

```{r}
library(rpart)
library(adabag)

set.seed(1234)
my.control <- rpart.control(xval=0, cp=0, minsplit=5, maxdepth=10)
bag.german <- bagging(y ~ . , data=german, mfinal=50, control=my.control)
summary(bag.german)
```

Variable Importance
```{r}
print(bag.german$importance)
importanceplot(bag.german)
```

Prediction
```{r}
pred.bag.german <- predict.bagging(bag.german, newdata=german)
head(pred.bag.german$prob,10)
```

Confusion matrix
```{r}
print(pred.bag.german$confusion)
```

(2) Boosting

```{r}
my.control <- rpart.control(xval=0,cp=0, maxdepth=1)
boo.german <- boosting(y ~ . , data=german, boos=T, mfinal=100, control=my.control)
summary(boo.german)
```

```{r}

evol.german = errorevol(boo.german, newdata=german)
plot.errorevol(evol.german)
```

(3) RandomForest
 - randomforest chooses some variable randomly instead of choosing all variables

Random Forest Fitting

```{r}
library(randomForest)
rf.german <- randomForest(y~., data=german, ntree= 100, mtry=5, importance=T, na.action=na.omit)
summary(rf.german)
```

Variable Importance
```{r}
importance(rf.german,type=1)
```

Prediction
```{r}
pred.rf.german <- predict(rf.german, newdata=german)
head(pred.rf.german,10)
```

Confusion matrix
```{r}
tab = table(german$y,pred.rf.german , dnn = c("Actual","Predicted"))
print(tab)
```

